---
title: "Built-in changepoint families"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Built-in changepoint families}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `cpd_family` argument chooses the interval loss and its model-fitting
protocol. This table mirrors the complete overview in the README and adds links
to the corresponding reference topics.

| Analysis | `cpd_family` | Recommended entry point | Selection |
| --- | --- | --- | --- |
| Mean changes | `"mean"` | `cv.reliever()` | CPSS outer CV for K |
| Covariance or joint mean/covariance changes | `"var"`, `"meanvar"` | `cv.reliever()` | CPSS outer CV for K |
| Linear or generalized linear model changes | `"lm"`, `"glm"` | `cv.reliever()` | CPSS outer CV for K |
| Exponential-family distribution changes | `"em"` | `cv.reliever()` | CPSS outer CV for K |
| Ordinary lasso path | `"lasso"` | `cv.reliever()` | CPSS for normalized lambda and K |
| Cross-fitting lasso | `"lasso_crossfit"` | `reliever()` | Interval-adaptive or homogeneous-hyperparameter ReCV |
| KDE negative log-likelihood | `"kde_nll"`, `"kde_nll_crossfit"` | `reliever()` | ReCV for data-driven bandwidth selection |
| Fixed-kernel KDE-L2 | `"kde_l2"` | `cv.reliever()` | CPSS outer CV for K |
| Univariate nonparametric CDF loss | `"nmcd"` | `cv.reliever()` | CPSS outer CV for K |
| Optional classifier losses | `"ranger_crossfit"`, `"mlp_crossfit"` | `reliever()` | Interval-adaptive or homogeneous-hyperparameter ReCV |

## NMCD with outer CV

NMCD detects general univariate distributional changes. Within outer CV, its
empirical reference is computed from the training observations in each fold.

```{r nmcd}
library(relieverChangepoint)

set.seed(2026)
n_seg <- 90L
x_nmcd <- c(
  rnorm(n_seg, mean = -4, sd = 0.35),
  rnorm(n_seg, mean = 4, sd = 0.35),
  rnorm(n_seg, mean = 0, sd = 0.35)
)

fit_nmcd <- cv.reliever(
  X = x_nmcd,
  cpd_family = "nmcd",
  cpn_max = 4,
  dm = 18,
  cov_rate = 0.7,
  method = "SN",
  nfolds = 5,
  dc_grid_size = 10
)

summary(fit_nmcd)
stopifnot(identical(summary(fit_nmcd)$K_hat, 2L))
```

## Fixed-kernel KDE-L2 with outer CV

KDE-L2 accepts either a kernel function or a precomputed kernel-evaluation
matrix. In the following interface, the Gaussian kernel and bandwidth are fixed
before CPSS selects K.

```{r kde-l2}
set.seed(2026)
n_seg <- 50L
x_kde <- c(
  rnorm(n_seg, mean = -3, sd = 0.45),
  rnorm(n_seg, mean = 3, sd = 0.45),
  rnorm(n_seg, mean = 0, sd = 0.45)
)

fit_kde <- cv.reliever(
  X = x_kde,
  cpd_family = "kde_l2",
  kernel = "gaussian",
  bandwidth = 0.8,
  cpn_max = 4,
  dm = 10,
  cov_rate = 0.6,
  method = "SN",
  nfolds = 5,
  dc_grid_size = 5
)

summary(fit_kde)
stopifnot(identical(summary(fit_kde)$K_hat, 2L))
```

For family-specific data types and arguments, open the relevant `reliever_*()`
or `reg_fun_*()` reference topic. The four main entry-point topics describe the
common search and selection controls once, avoiding repeated parameter text.
