---
title: "Get started with relieverChangepoint"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with relieverChangepoint}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`relieverChangepoint` fits changepoint paths efficiently when fitting a model
on every possible interval would be costly. The package also supplies several
ways to select model settings and the number of changepoints, denoted by K.

## Choose an entry point

For most first analyses, use `cv.reliever()`. It uses CPSS outer
cross-validation to select K and then automatically refits the selected path on
all observations.

| Task | Entry point |
| --- | --- |
| Select K for an ordinary built-in family | `cv.reliever()` |
| Retain a complete built-in candidate path | `reliever()` |
| Fit a custom interval loss | `reliever_generic()` |
| Apply outer CV to a compatible custom loss | `cv.reliever_generic()` |

The cross-fitted families use a different selection workflow, described in
[Model and K selection](selection-workflows.html).

## A complete mean-change analysis

The following series has changepoints after observations 100 and 200.

```{r mean-data}
library(relieverChangepoint)

set.seed(2026)
n_seg <- 100L
x <- c(
  rnorm(n_seg, mean = 0, sd = 0.5),
  rnorm(n_seg, mean = 4, sd = 0.5),
  rnorm(n_seg, mean = -4, sd = 0.5)
)
```

Fit, select K, and refit on all observations in one call:

```{r mean-fit}
fit <- cv.reliever(
  X = x,
  cpn_max = 4,
  dm = 15,
  cov_rate = 0.7,
  method = "SN",
  nfolds = 5,
  dc_grid_size = 10
)

summary(fit)
stopifnot(identical(summary(fit)$K_hat, 2L))
```

`fit$full_data_fit` is the final full-data changepoint fit. There is no need to
call `reliever()` again.

```{r mean-plot, fig.width=7, fig.height=4}
plot_reliever_data(result = fit, data = x)
```

## Keep the whole path instead

Use `reliever()` when you want all candidate segmentations or intend to apply a
post-fit selection rule.

```{r mean-path}
path <- reliever(
  X = x,
  cpn_max = 4,
  dm = 15,
  cov_rate = 0.7,
  method = "SN",
  dc_grid_size = 10
)

path$cpd_path$candidates
select_by_run(result = path, cpn_crit = "rss_sic")
```

Next, see the [selection guide](selection-workflows.html) and the complete
[built-in family guide](built-in-families.html).
